---
title: "Scaling Models for Textual Data"
author: "Ken Benoit"
date: "ANU 5-6 November 2020"  
output:
  xaringan::moon_reader:
    css: [default, default-fonts, css/styles.css]
    lib_dir: libs
    toc: true
    toc_depth: 2
    number_sections: true
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


## Scaling: unsupervised and supervised

Supervised
-  Wordscores
-  "class affinity scaling"

Unsupervised
-  Wordfish
-  Correspondence Analysis

---

## Supervised scaling

```{r echo = FALSE}
suppressMessages(library("quanteda", quietly = TRUE, warn.conflicts = FALSE))
library("quanteda.textmodels")
```

```{r}
tmod <- textmodel_wordscores(data_dfm_lbgexample, y = c(seq(-1.5, 1.5, .75), NA))
summary(tmod)
```

---

## Extracting useful information

```{r}
coef(tmod)
```

---

## Predictions

```{r}
predict(tmod)
predict(tmod, newdata = data_dfm_lbgexample["V1", ])
predict(tmod, rescaling = "lbg")
```

---

## Predictions with confidence intervals

```{r}
predict(tmod, se.fit = TRUE, interval = "confidence", rescaling = "mv")
```

---

## Plotting a textmodel

```{r}
dfmat <- dfm(data_corpus_irishbudget2010)
refscores <- c(rep(NA, 4), 1, -1, rep(NA, 8))
tmod1 <- textmodel_wordscores(dfmat, y = refscores, smooth = 1)
```

---

## Plotting a textmodel

```{r}
# plot estimated document positions
textplot_scale1d(predict(tmod1, se.fit = TRUE), 
                 groups = dfmat$party)
```

---

## Unsupervised method: Wordfish

-  Does not require reference texts
-  Estimates a latent position for each text, represented as $$\theta$$
-  Estimates word weights and word "coefficients"
-  Includes confidence intervals
-  No "predict" step

---

## Fitting the Wordfish model

```{r}
dfmat <- dfm(data_corpus_irishbudget2010)
tmod2 <- textmodel_wordfish(dfmat, dir = c(6,5))
summary(tmod2)
```

---

## Plotting the Wordfish model

```{r}
textplot_scale1d(tmod2, groups = dfmat$party)
```

---

## Other textmodel types

-  `textmodel_affinity`: Class affinity maximum likelihood text scaling model
-  `textmodel_ca`: Correspondence analysis of a document-feature matrix
-  `textmodel_lsa`: Latent Semantic Analysis
