---
title: "Scaling Models for Textual Data"
author: "Ken Benoit"
date: "ANU 5-6 November 2020"  
output:
  xaringan::moon_reader:
    css: [default, default-fonts, css/styles.css]
    lib_dir: libs
    toc: true
    toc_depth: 2
    number_sections: true
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


## Scaling: unsupervised and supervised

Supervised
-  Wordscores
-  "class affinity scaling"

Unsupervised
-  Wordfish
-  Correspondence Analysis

---

## Supervised scaling

```{r echo = FALSE}
suppressMessages(library("quanteda", quietly = TRUE, warn.conflicts = FALSE))
library("quanteda.textmodels")
```

```{r}
tmod <- textmodel_wordscores(data_dfm_lbgexample, y = c(seq(-1.5, 1.5, .75), NA))
summary(tmod)
```

---

## Extracting useful information

```{r}
coef(tmod)
```

---

## Predictions

```{r}
predict(tmod)
predict(tmod, newdata = data_dfm_lbgexample["V1", ])
predict(tmod, rescaling = "lbg")
```

---

## Predictions with confidence intervals

```{r}
predict(tmod, se.fit = TRUE, interval = "confidence", rescaling = "mv")
```

---

## Plotting a textmodel

```{r}
dfmat <- dfm(data_corpus_irishbudget2010)
refscores <- c(rep(NA, 4), 1, -1, rep(NA, 8))
tmod1 <- textmodel_wordscores(dfmat, y = refscores, smooth = 1)
```

---

## Plotting a textmodel

```{r}
# plot estimated document positions
textplot_scale1d(predict(tmod1, se.fit = TRUE), 
                 groups = dfmat$party)
```

---

## Unsupervised method: Wordfish

-  Does not require reference texts
-  Estimates a latent position for each text, represented as $$\theta$$
-  Estimates word weights and word "coefficients"
-  Includes confidence intervals
-  No "predict" step

---

## Fitting the Wordfish model

```{r}
dfmat <- dfm(data_corpus_irishbudget2010)
tmod_wf <- textmodel_wordfish(dfmat, dir = c(6, 5))
summary(tmod_wf)
```

---

## Plotting the Wordfish model

```{r}
textplot_scale1d(tmod_wf, groups = dfmat$party)
```

---

## Other textmodel types

-  `textmodel_affinity`: Class affinity maximum likelihood text scaling model
-  `textmodel_ca`: Correspondence analysis of a document-feature matrix
-  `textmodel_lsa`: Latent Semantic Analysis

---

```{r}
tmod_ca <- textmodel_ca(dfmat)

# plot comparison of two document scores
plot(coef(tmod_wf, "doc")[, "theta"], coef(tmod_ca)$coef_document,
     xlab = "Wordfish document positions",
     ylab = "CA document positions")
```
---

```{r}
# plot comparison of two word positions
plot(coef(tmod_wf, "features")[, "beta"], coef(tmod_ca)$coef_feature,
     xlab = "Wordfish feature weights",
     ylab = "CA feature weights")
```
---

Scaling plot of document positions for Wordfish:
```{r}
textplot_scale1d(tmod_wf, groups = dfmat$party)
```
---

Compare with correspondence analysis:
```{r}
textplot_scale1d(tmod_ca, groups = dfmat$party)
```

---
We can also plot the scaling figures for features.
```{r}
textplot_scale1d(tmod_wf, margin = "features",
                 highlighted = c("gang", "bailout", "medicine", 
                                 "stabilise", "innovation", "future"))
```

